\chapter{Conclusions to part II}
\label{ch:summary2}

The contributions to the calibration and upgrade of the CMS pixel barrel detector have been presented in this part of thesis.
First, a major effort was made during the first long shut-down to recover the full detector performance after the first LHC physics run.
This effort included the replacement of broken components and the recalibration of detector parameters at low temperature needed to compensate for the effects of radiation damage.
The detector was reinstalled into CMS in December 2014 and commissioned in January 2015 for the second LHC physics run at the highest center-of-mass energy of 13\TeV.
The expertise gained during the long shut-down helped guaranteeing the success of the entire operation, which was completed in only a few weeks.
%The entire operation was completed in only a few weeks thanks to the expertise gained during the long shut-down.
The first pp collision at 13\TeV occurred on March, 21st 2015 and since then the detector
%showed excellent performance.
has been running stable with a high data-taking efficiency.
%Its conditions and performance were monitored during the first two years of data-taking after reinstallation and they have been excellent.
%This has been made possible thanks to recalibrations that happened throughout 2015 and 2016.

Furthermore, I contributed to the Phase 1 upgrade pixel project.
The upgraded detector will allow CMS to maintain its excellent tracking performance at the upcoming higher luminosity conditions at the LHC.
A test stand at the University of Zurich has been set up and operated with the aim of testing the performance of the components of the upgraded pixel system and gain experience in its operations. The setup includes a full slice of the CMS pixel detector system, including DAQ together with all the upgraded electronics for the power, readout and control systems as well as the newly developed pixel modules.
The test system has been employed to implement and test new developments in the pixel online software used to operate with the detector.
Although the software architecture remains unchanged, several calibration procedures for the original detector become obsolete with the new digital readout of the upgraded system,
whereas novel tests have been developed. 
Additional fundamental modifications had to be understood and implemented in order to operate the software with the upgraded detector.
The new detector has been recently installed into CMS in the spring of 2017 and it will start taking data in the summer.
The novel calibration procedures helped guarantee the success of the integration, installation and commissioning of the detector.