\chapter{Conclusions}
\label{ch:summary1}

A search for new massive resonances decaying into a pair of vector bosons (WW/WZ) or into a W boson and a Higgs boson (WH)
in lepton+jet final states has been presented. In particular two analyses and a statistical combination with previous searches have been described.

The first analysis is performed with pp collision data at $\sqrt{s} = 8\TeV$ collected in 2012, and is focused on the final state given by the W-boson decay to $\ell\nu$, with $\ell$ = $\mu$ or e,
and the Higgs boson decay to a pair of bottom quarks.
The second analysis is performed with pp collision data at $\sqrt{s} = 13\TeV$ collected in 2015, and also in this case a final state is considered given by the $\PW\to\ell\nu$ decay together with the decay of the second boson into quarks, where the second boson (V) can be either a W or a Z. 

In both analyses, each event is reconstructed as a leptonic W-boson candidate recoiling against a jet with mass compatible with the H- or V-boson mass for the $\ell\nu\bbbar$ or $\ell\nu\qqbar$ analysis channel, respectively.
Specialized methods, referred to as V tagging and H tagging, are exploited to help resolve jet decays of massive bosons and achieve a large suppression of background from the W+jets process.
In particular, the H-tagging algorithm combines jet-substructure information with identification techniques based on the peculiarities of b jets.

In the $\ell\nu\bbbar$ analysis channel, no excess of events above the standard model prediction is observed in the muon channel,
while an excess with a local significance of 2.9 standard deviations is observed in the electron channel at $\mWH \approx 1.8\TeV$.
Taking into account the look-elsewhere effect, the results are statistically compatible with the standard model within 2 standard deviations.
In the context of the little Higgs and the heavy vector triplet models, upper limits at 95\% CL are set on the \Wpr production cross section
in a range from 100 to 10\unit{fb} for masses between 0.8 and 2.5\TeV, respectively.
Within the little Higgs model, a lower limit on the \Wpr mass of 1.4\TeV has been set.
A HVT model that mimics the properties of composite Higgs models has been excluded up to a \Wpr mass of 1.5\TeV.

These results are improved by the limits set by the analysis in the $\ell\nu\qqbar$ decay channel.
No evidence for a signal is found in this search with new 2015 data, and the result is interpreted as an upper limit on the production cross section of a narrow-width resonance as a function of its mass,
in the context of several benchmark models for spin-1 and spin-2 resonances. In particular, for the same HVT model as mentioned above the data exclude a $\Wpr$ resonance with masses $< 1.9\TeV$.

However, the best results are provided by a statistical combination of all searches performed in CMS with 8 and 13\TeV data for massive resonances decaying to pairs of W, Z, and Higgs bosons in various final states.
The results are interpreted in the context of heavy-vector singlet and triplet models predicting a \Wpr and a \Zpr decaying to WZ, WH, WW, and ZH and a model with a bulk graviton that decays into WW and ZZ.
The combined significance of a potential resonance with a mass between 1.8 and 2.0\TeV has been evaluated and has been found to be 0.8 standard deviations for the hypothesis of a \Wpr,
thus the excesses observed in the $\ell\nu\bbbar$ channel in 8\TeV data is not confirmed.
The combination yields mass limits at the 95\% CL on a spin-1 resonance in the range 2.2--2.4\TeV, depending on the specific benchmark.
The most stringent cross-section limits on a narrow-width bulk graviton resonance with $\tilde{k} = 0.5$ to date are set in the mass range from 0.6 to 4\TeV.
